The Language of Generalization

### 2018-12-12 paper/comgen-paper.tex
reorganize data folder, proof edits to ms

\authornote{This paper is currently under review. Comments or
suggestions are appreciated and should be directed to MHT.

>>>>

\authornote{This paper is based on a Ph.D.~dissertation
submitted to Stanford University. The research was supported by National
Science Foundation Graduate Research Fellowship DGE-114747 awarded to
MHT and DARPA PPAML grant FA8750-14-2-0009 to NDG. A portion of this
paper (Case Study 2) appeared in the proceedings of the 38th Annual
Meeting of the Cognitive Science Society, Philadelphia, 2016. We are
deeply grateful to Ellen Markman, Gregory Scontras, Thomas Icard,
Michael C. Frank, and Sophie Bridgers for extensive conversations and
support for this work. In addition, the work was greatly improved
through countless discussions with members of the Computation and
Cognition Lab and the Language and Cognition Lab at Stanford, as well as
the participants of \emph{A Generic Workshop} at the Center for the
Study of Language and Information (CSLI) at Stanford in May 2017.
Finally, we thank two anonymous reviewers and Joshua Hartshorne for
helping us clarify our main arguments and improving the quality of the
manuscript.
